Hydras \& Co.

### 2022-02-21 doc/gaia-chapter.tex
Add MathComp's finite ordinals to ON instances

\section{Library structure}
The \gaiaHydras library is designed for use  by users of
\gaia and/or  \HydrasLib. Whenever possible, we managed to respect the notations and naming conventions of both libraries.

@@

\begin{todo}
Give equations for \texttt{canon} (corresponding to the structural recursive definition in \HydrasLib.
\end{todo}

The following lemmas are proved by rewriting from corresponding statements proved in \HydrasLib.
\inputsnippets{GCanon/g2hCanonRw}

>>>>

\section{Library structure}
The \gaiaHydras library is designed for users of
\gaia and/or  \HydrasLib. Whenever possible, we managed to respect the notations and naming conventions of both libraries.

@@

\inputsnippets{GCanon/g2hCanonRw}

The following lemmas are proved by rewriting from corresponding statements proved in \HydrasLib. The first six lemmas correspond to rewriting rules derived from the body of the definition of \texttt{Epsilon0.Canon.canon}.
